Dark energy is based on a math error from 1930

### 2024-12-26 paper/paper.tex

The measurement of Type Ia supernovae is one of the primary sources of data for
cosmological models. The measurements involve estimating the peak magnitude in
the B filter \citet{riess1998} for the rest frame, meaning we want to know how
bright the SnIa would be if its light didn't undergo redshift. Redshift causes
the light that would be mesaured by the B filter in a rest frame to be shifted
to another filter. In order to observe a SnIa in an arbitrary filter and report
the magnitude in filter B, we use a technique called k-corrections.

The first formal derivation of k-corrections was performed by
\citet{tollman1930}, and it failed to account for bandwidth stretching, one of
the dimming effects of redshift. This error was noted by \citet{desitter1934},
but in \citet{hubble1935} the descrepancy was noted and ignored.
\citet{oke1968} rederived k-corrections, but they failed to account time
dilation, one of the other dimming effects of redshift. In \citet{kim1996},
k-corrections were extended to handle additional cross-filter comparisons and
address zero-point corrections, but they started their derivation by
referencing the incorrect equation from \citet{oke1968}. \citet{hsiao2007}
expanded on the work done by \citet{kim1996} by providing expected SnIa
template spectra.  Finally, \citet{burns2010} implemented the popular software
package Sn(OO)py which implemented the SnIa template spectra into
k-corrections. This software package computes k-corrections differently from
prior work, and in order to match prior values, the code adds an extra term.
This history is explored in more depth in Section \ref{sec:history}.

@@

A few years later, \citet{desitter1934}, discussed all three issues that would
reduce the observed magnitude of a distant observation. The correction for each
of these issues is identical: take a measurement for luminosity and multiply it
by the factor $1 + z$.

@@

\begin{figure}[h]
  \includegraphics[width=\linewidth]{k-corrections_for_photon_counts.png}
  \caption{An example of how k-corrections take an observed spectrum and
  produce a rest-frame spectrum. [TODO]
  }
  \label{fig:k-example}
\end{figure}

The modern treatment of k-corrections is based on the work of \citet{kim1996}.

\lstinputlisting[language=Python, caption=A demonstration that k-corrections
calculated by snpy are off by \texttt{2.5*log10(1+z)}. The roundoff error is
roughly \texttt{2e-16}.]{code_listing.py}

>>>>

The measurement of Type Ia supernovae is one of the primary sources of data for
cosmological models. The measurements involve estimating the peak magnitude in
the B filter \citet{riess1998} for the rest frame, meaning we want to know how
bright the SnIa would be if its light didn't undergo redshift. Redshift causes
the light that would be mesaured by the B filter in a rest frame to be shifted
to another filter. In order to observe a SnIa in an arbitrary filter and report
the magnitude in the B filter we use a technique called k-corrections.

The first formal derivation of k-corrections was performed by
\citet{tollman1930}, and it failed to account for bandwidth stretching, one of
the dimming effects of redshift. This error was noted by \citet{desitter1934},
but in \citet{hubble1935} the descrepancy was noted and ignored.
\citet{oke1968} rederived k-corrections, but they failed to account for time
dilation, one of the other dimming effects of redshift. In \citet{kim1996},
k-corrections were extended to handle additional cross-filter comparisons and
address zero-point corrections, but they started their derivation by
referencing the incorrect equation from \citet{oke1968}. \citet{hsiao2007}
expanded on the work done by \citet{kim1996} by providing expected SnIa
template spectra. Finally, \citet{burns2010} implemented the popular software
package Sn(OO)py which implemented the SnIa template spectra into
k-corrections. This software package computes k-corrections differently from
prior work, and in order to match prior values, the code adds an extra term.
This history is explored in more depth in Section \ref{sec:history}.

@@

A few years later, \citet{desitter1934}, discussed all three issues that reduce
the observed magnitude of a distant observation. The correction for each of
these issues is identical: take a measurement for luminosity and multiply it by
the factor $1 + z$.

@@

\begin{figure}[h]
  \includegraphics[width=\linewidth]{k-corrections_for_photon_counts.png}
  \caption{An example of how k-corrections take an observed magnitude and
  produce a rest frame magnitude. In this example, $z=1$. The observation
  filter measures magnitude, which is equivalent to measuring the number of
  photons per nanometer. In the bottom left panel, a correction of $1+z$ is
  applied which doubles the photons per nanometer. The top right panel shows
  the effect of correcting for the bandwidth spectrum warping effect --
  correcting all wavelengths for the rest frame means that the measured
  wavelengths have blueshifted, ideally into the cross band B filter. Applying
  both effects, shown in the bottom right panel, requires applying two
  correction factors of $1+z$. This example omits the correction for a similar
  effect related to lower energy due to the Planck relation because CCD cameras
  obviate the need to correct for this effect.
  }
  \label{fig:k-example}
\end{figure}

The modern treatment of k-corrections is based on the work of \citet{kim1996}.
This work extended the calculations of k-corrections to extend to filters
beyond B and V. It also introduced a term that deals with the zero-point for the
actual filters. Equation 2 from this paper is the form of the k-corrections
used in the modern day:

\begin{equation}
  K_{xy} = -2.5\text{log} \left(\frac{\int \mathcal{Z}(\lambda)S_x(\lambda)d\lambda}{\int \mathcal{Z}(\lambda)S_y(\lambda)d\lambda}\right) + 2.5\text{log}(1+z) + 2.5\text{log}\left(\frac{F(\lambda)S_x(\lambda)d\lambda}{F(1/(1+z))S_y(\lambda))d\lambda}\right).
\end{equation}

The first term of this equation deals with zero-points, which is a magnitude
added to individual filters to correct for the light gathering abilities of the
telescope. The third term measures the flux in the observation filter and divides it by  the flux that would be measured

The next major advance in k-corrections was

\citet{snpy}

\begin{minipage}[c]{0.95\textwidth}
\lstinputlisting[language=Python, caption=A demonstration that k-corrections
calculated by snpy are off by \texttt{2.5*log10(1+z)}. The roundoff error is
roughly \texttt{2e-16}.]{code_listing.py}
\end{minipage}
